Derivation of Variational Bayes

### 2016-09-22 written report/ar1_predictive.tex
updates

@@

A Metropolis Hastings MCMC scheme was set up using a random walk candidate distribution for $\psi$ to draw from $p(\mu | y_{1:T}), p(\sigma^2 | y_{1:T})$ and $p(\psi | y_{1:T})$. These draws were then sampled to find the distribution of $p(y_{T+1} | y_{1:T})$.
The chain had 1000 burn in draws followed by 50000 kept draws and took 6.736 seconds to complete the chain and forecast distribution.

\begin{figure}[hb]
\centering
\includegraphics{ar1_predictive-plots}
\caption{Variational approximation for $q(y_{T+1}|y_{1:T})$ (blue) and the MCMC density for $p(y_{T+1}|y_{1:T})$ (red). 
The KL Divergence from q to p is 0.015, and from p to q is 0.018.}
\label{densities}
\end{figure}

\end{document}

>>>>

Note: Code uses a stretched beta, latex math still uses regular beta.

@@
